---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Demo R Data Package

Disclaimer: This is the skeleton of an `R` data package used in the talk ["Teaching Data Sharing with `R` Data Packages"](https://mcconvil.github.io/r-data-package-talk-f25/data_packages_talk).  This is not a fully fleshed out package.  

# jeans

The goal of `jeans` is to make jeans shopping easier and less stressful by providing a tidy dataset of several jeans you can purchase online from [Anthropologie](https://www.anthropologie.com/).


## Installation

You can install the development version of `jeans` from [GitHub](https://github.com/mcconvil/jeans) with:

```{r}
# install.packages("pak")
pak::pak("mcconvil/jeans")
```

## Example

Here's a simple example where we are determining the least expensive pair of jeans in the dataset.

```{r example}
library(jeans)
# Cheapest pair of jeans
jeans |>
  dplyr::slice_min(order_by = cost)
```



